Concurrent Programming with CXL

### 2020-05-18 book/paper.tex
Adding discussion of methods and pointers

\chapter{CXL Values}

@@

>>>>

\chapter{CXL Values}
\label{ch:cxlvalues}

@@

You may note that all this looks familiar.  Indeed, the syntax
is the same as that for dictionaries (see Chapter~\ref{ch:cxlvalues}).
Both dictionaries and methods map CXL values to CXL values,
and their syntax is indistinguishable.
If \texttt{f} is either a method or a
dictionary, and \texttt{x} is an arbitrary CXL value, then
then \texttt{f x}, \texttt{f(x)}, and \texttt{f[x]} are all
the same expression in CXL.

CXL is not an object-oriented language like Python is.  In Python
you can pass a reference to an object to a method, and that method
can then update the object.  In CXL, it is also sometimes convenient
to have a method update a shared variable specified as an argument.
For this (as well as some other uses), CXL supports \emph{pointers}
to shared variables.
If \texttt{x} is a shared variable, then the expression \texttt{\&(x)}
(the parentheses are mandatory) is a pointer to \texttt{x}
(also known as the \emph{address} of \texttt{x}.
Conversely, if \texttt{p} is a pointer to a shared variable, then the
expression \texttt{\^{}p} is the value of the shared variable.
